---
title: "rMAUPS: Analysis of Potential for Ubiquitination"
author:
- name: Collin Tokheim, Wubing Zhang, Jun Ge, X. Shirley Liu
  affiliation: Dana-Farber Cancer Institute
package: "rMAUPS - 0.1.1"
output:
  BiocStyle::html_document
vignette: |
  %\VignetteIndexEntry{Ubiquitin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This vignette assumes that you have already properly installed rMAUPS.

# Searching protein sequence

First, load the rMAUPS package.

```{r libs, warning=FALSE}
library(rMAUPS)
```

Next, read in protein sequences from uniprot.

```{r listfile}
uniprot_path <- system.file("extdata", "human_uniprot_seq.txt", package = "rMAUPS")
uniprot <- read.delim(uniprot_path, sep='\t')
head(uniprot)
```

Next, search the protein sequences for lysine residues ("K"). 

```{r search}
lysine_pos <- searchProtSeq(head(uniprot), 'K')
head(lysine_pos)
```

Note, for the sake of a quick example, the above command only searched against the top few protein sequences. Additionally, although not used here, the searchProtSeq function can also handle searching for sequences using regular expression.

# Viewing protein structure

First, we'll view all of the lysine residues for KRAS.

```{r viewProt}
# get hits for P01116
id <- 'P01116'
start <- lysine_pos[lysine_pos['UniprotId']==id, 'start']
end <- lysine_pos[lysine_pos['UniprotId']==id, 'end']

# view on protein structure
browseProtStructure(id, start, end)
```

Next, we'll compare those to the lysines with reported ubiquitination sites.

```{r viewProtUb}
# Here, we manually create a dataframe for the KRAS ubiqutination sites.
# In the realisitic scenario, you should load the "Ubiquitination_site_dataset" file
# from PhosphositePlus DB using the readPSPUbiquitin function. You'll need to download
# it your self due to copy protection.
id <- 'P01116'
ub <- data.frame(gene='KRAS', ID=id, position=c(117, 128, 147))

# get ub sites for P01116
start <- ub[ub['ID']==id, 'position']
end <- ub[ub['ID']==id, 'position']

# view on protein structure
browseProtStructure(id, start, end)
```

# Session info

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
